Grade Retention and Mixed Race

### 2022-09-05 products/paper/main.qmd
Add counterfactual probability placement table

>>>>

|                   | Lower than both | Same as lower | Between | Same as higher | Higher than both |
|-------------------|:---------------:|:-------------:|:-------:|:--------------:|:----------------:|
| White/Asian       |       X         |               |         |                |                  |
| Black/Asian       |                 |  X  (Asian)   |         |                |                  |
| Black/Latino      |                 |  X  (Black)   |         |                |                  |
| White/Latino      |                 |  X  (White)   |         |                |                  |
| Indigenous/Latino |                 |  X  (Indig.)  |         |                |                  |
| Latino/Asian      |                 |  X  (Asian)   |         |                |                  |
| White/Indigenous  |                 |               |    X    |                |                  |
| Indigenous/Asian  |                 |               |    X    |                |                  |
| Black/Indigenous  |                 |               |    X    |                |                  |
| Black/White       |                 |               |         |   X (Black)    |                  |

: Relative placement for biracial groups in comparison to monoracial constituent groups of counterfactual predicted probability of being held back based due to resources.
